What's hot and what's not:\\Windowed developer topic analysis

### 2009-06-15 lda-paper.tex

>>>>

\section{Real Introduction}

We care about the topics of development. We want to know given a
certain period of time, what were the popular topics being worked on
during that period. We also want to know if any of those topics
occurred again, whether before or after our current period.

These topics could help stakeholders determine what their coworkers
were working on, what were common issues, what requirements were being
worked on, etc.

Topic analysis extracts groups of words from documents (commit log
comments) that are word distributions, topics, which characterize
clusters of documents. These extracted topics often correlate with
actual development topics that the developers discussed.

Usually topic analysis is applied to the entire history of a project,
where as we suggest that more topics are probably local, if a
programmer is working on a story card, they might never deal with that
story card ever again. Thus that topic might be quite relevant to a
small window of time but never relevant ever again.  By applying topic
analysis locally to an iteration, both the developers and managers
might be able to see what were the topics of development during that
iteration, rather than the whole project.

Topic analysis often allows for a single document, such as a commit
message, to be related to multiple documents. This maps well to
commits which often have more than one purpose.

Commits in source control systems (SCSs) can have multiple
purposes. Thus we hope that our research will help uncover these
multiple purposes that manifest themselves as topics interleaved
within the commits.  Others have demonstrated that topic analysis
techniques, such as Latent Semantic Indexing (LSI) and Latent
Dirichlet Allocation (LDA), can aid in separating topics from these
mixed comments. These topics often describe distinct ideas that are
interleaved throughout the development. A topic represents both a word
distribution and a group of commit log comments that are related to
each other by their content.  In this case a topic is a set of tokens.
